The Analogue Method for Precipitation Forecasting: Finding Better Analogue Situations at a Sub-Daily Time Step

### 2015-12-16 Moving temporal window - HESS/template.tex
Writing the Moving temporal window.

\begin{table}[h]
	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the sliding time window. The changes are presented for both 2Z and 2Z-2MI methods with the original parameters. A decrease of the score is desirable.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_no_recalibration}
\end{table}

\begin{table}[h]
	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_recalibration}
\end{table}

\begin{figure*}[h]
	\begin{center}$
		\begin{array}{cccc}
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse.pdf} &
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse.pdf} &
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse.pdf} &
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse.pdf} \\
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_justesse_recalib.pdf} &
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R1_finesse_recalib.pdf} &
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_justesse_recalib.pdf} &
		\includegraphics[width=4cm]{figures/Graphique_fenetre_glissante_comp_R2_finesse_recalib.pdf} 
		\end{array}$
	\end{center}
	\caption{Influence de la fenêtre temporelle glissante sur les composantes du CRPS (justesse et finesse), pour les méthodes R1 et R2. Les résultats sont présentés pour (haut) les paramètres originaux et (bas) recalibrés. Une amélioration de la prévision se traduit par une baisse du score.}
	\label{fig:Graphique_fenetre_glissante_crps_comp}
\end{figure*}

Il apparaît que la finesse est moins bonne avec la fenêtre temporelle glissante, au profit de la justesse, et ceci pour les mêmes paramètres que la méthode standard, alors qu'elle décroît avec l'augmentation du nombre d'analogues après recalibration. La Figure \ref{fig:Graphique_fenetre_glissante_crps_comp}, illustrant les changements en finesse et justesse pour différentes gammes de précipitations à la station d'Ulrichen, présente cette même tendance. Nous y voyons également que le plus grand gain en justesse concerne les gammes de précipitations les plus importantes, que ce soit pour R1 ou R2.  La fenêtre temporelle glissante ne permet donc pas d'améliorer la finesse, mais l'amélioration de la justesse est significative, et ceci notamment pour les jours de fortes précipitations. Cela signifie donc que le quantile 50~\% de la distribution prévue se rapproche des cumuls observés, mais que la distribution n'est pas plus condensée que précédemment.

\section{Tentatives d'application à l'archive complète}

>>>>

\begin{table}[htb]
	\caption{Changes in sharpness and accuracy relatively to the total CRPS, due to the introduction of the sliding time window. The changes are presented for both 2Z and 2Z-2MI methods with the original parameters. A decrease of the score is desirable.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 2.82 & -5.29 & 1.00 & -4.30 \\
			Zermatt & 2.26 & -5.01 & 0.88 & -3.58 \\
			Visp & 3.66 & -5.18 & 2.67 & -4.94 \\
			Montana & 1.62 & -2.78 & 0.57 & -2.91 \\
			Sion & 2.02 & -2.78 & 0.33 & -2.75 \\
			Aigle & 0.52 & -2.26 & -1.20 & -2.17 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_no_recalibration}
\end{table}

\begin{table}[htb]
	\caption{Same as Table \ref{table:CRPSS_decomposition_no_recalibration} but with the re-calibrated parameters.}
	\begin{center}
		\begin{tabular}{l c c c c}
			\hline
			\multirow{2}{*}{Station} & \multicolumn{2}{c}{2Z} & \multicolumn{2}{c}{2Z-2MI} \\
			& Sharpness & Accuracy & Sharpness & Accuracy \\
			\hline
			Ulrichen & 1.44 & -4.56 & -0.37 & -3.34 \\
			Zermatt & 0.80 & -4.03 & 0.75 & -4.42 \\
			Visp & 1.53 & -3.94 & 1.47 & -4.96 \\
			Montana & -0.27 & -1.80 & 0.06 & -3.71 \\
			Sion & 0.95 & -2.66 & -0.10 & -3.19 \\
			Aigle & -0.35 & -2.01 & -2.08 & -1.90 \\ 
			\hline
		\end{tabular}
	\end{center}
	\label{table:CRPSS_decomposition_recalibration}
\end{table}

\begin{figure*}[htb]
	\begin{center}$
		\begin{array}{cccc}
		\includegraphics[width=4cm]{figures/component_2Z_accuracy.pdf} &
		\includegraphics[width=4cm]{figures/component_2Z_sharpness.pdf} &
		\includegraphics[width=4cm]{figures/component_2Z-2MI_accuracy.pdf} &
		\includegraphics[width=4cm]{figures/component_2Z-2MI_sharpness.pdf} \\ \\
		\includegraphics[width=4cm]{figures/component_2Z_accuracy_recalib.pdf} &
		\includegraphics[width=4cm]{figures/component_2Z_sharpness_recalib.pdf} &
		\includegraphics[width=4cm]{figures/component_2Z-2MI_accuracy_recalib.pdf} &
		\includegraphics[width=4cm]{figures/component_2Z-2MI_sharpness_recalib.pdf} 
		\end{array}$
	\end{center}
	\caption{Influence (\%) of the STW on the CRPS components (accuracy and sharpness) relatively to the total CRPS, for the 2Z and 2Z-2MI methods, according to different precipitation thresholds. The results are presented for (top) the original parameters, and (bottom) the recalibrated parameters. Improved prediction results in a lower score.}
	\label{fig:CRPSS_decomposition_precip_thresholds}
\end{figure*}

It appears that the sharpness is a bit inferior with the STW in favor of accuracy (Table \ref{table:CRPSS_decomposition_no_recalibration}). When using the recalibrated parameters, the components are a bit more balanced, but still the accuracy prevails on the sharpness (Table \ref{table:CRPSS_decomposition_recalibration}). Figure \ref{fig:CRPSS_decomposition_precip_thresholds} illustrates the changes (relative to the total CRPS) in sharpness and accuracy for different precipitation thresholds at the Ulrichen station. Be it for the 2Z or 2Z-2MI method, the original or the recalibrated parameters, the changes are similar: the improvements concern the accuracy over the sharpness, and this to a greater extent for significant precipitation events. The STW does not allow to improve the sharpness, but the improvement in accuracy is significant, and this especially for the days with heavy precipitation. In terms of the predicted precipitation distribution, it means that the median of the prediction is closer to the observed values, but the distribution is not more condensed than previously.

\section{Application attempts on the full archive}
